Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-12-20 WSSSPE3/report/wg_appendix_best_practices.tex
moved all emails to footnotes for consistency

Sandra Gesing\footnote{email:\href{mailto:sandra.gesing@nd.edu}{sandra.gesing@nd.edu}} will serve as
the point of contact for this working group, and be responsible for ensuring timely progress of the planned actions.

>>>>

Sandra Gesing\footnote{email: \href{mailto:sandra.gesing@nd.edu}{sandra.gesing@nd.edu}} will serve as
the point of contact for this working group, and be responsible for ensuring timely progress of the planned actions.

### 2015-12-20 WSSSPE3/report/wg_main_metrics.tex
some general cleanup/consistency
moved all emails to footnotes for consistency

The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software including
addressing if there is a common set of metrics that can be filtered in some way,
can metrics be fit into a common template, which metrics would be the most
useful for each stakeholder, which metrics are the most helpful and how would we
assess this, how are metrics monitored, and many more. A more complete bulleted
list of these questions can be found in Appendix H. Next, a roadmap for how to
proceed was discussed including creating a set of milestones and tasks. The idea
was put forth for the group to interact with the organizing committee of the
2016 NSF Software Infrastructure for Sustained Innovation (SI2) PI workshop in
order to send a software metrics survey to all SI2 and related awardees as a
targeted and relevant set of stakeholders. The five solicitations for software
elements released under the NSF SI2 program all included metrics as a required
component with submitters requested to include {\it ``a list of tangible metrics,
with end user involvement, to be used to measure the success of the software
element developed, \dots''}. These metrics are then reported as part of annual
reports to NSF by the projects. Although neither the proposal text describing
the metrics nor the reported metric results are publicly available, there is
reason to believe that the community will be willing to provide this information
through a survey mechanism. This survey would be created by one of the student
group members. Similarly, it was suggested that a software metrics survey be
sent to the UK SFTF (Software For The Future, led by the Engineering and Physical Sciences Research Council) and TRDF (Tools and Resources Development Fund, led by the Biotechnology and Biological Sciences Research Council) software projects to ask them what metrics would be useful to report. The remainder of the discussion focused mainly on the creation
of a white paper on this topic. This resulted in a paper outline and writing
assignments with the goal of publishing in venues including WSSSPE4, IEEE CiSE (Institute of Electrical and Electronic Engineers Computing in Science and Engineering magazine), or JORS (Journal of Open Research Software). More information about the group discussion is available in Appendix~\ref{sec:appendix_metrics}

@@

In lieu of a landing page, the Useful Metrics for Scientific Software working
group requests an email be sent to Gabrielle Allen
\href{mailto:gdallen@illinois.edu}{(gdallen@illinois.edu)} to find out more
about the group's efforts and how to participate.

>>>>

The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software including
addressing if there is a common set of metrics that can be filtered in some way,
can metrics be fit into a common template, which metrics would be the most
useful for each stakeholder, which metrics are the most helpful and how would we
assess this, how are metrics monitored, and many more. A more complete bulleted
list of these questions can be found in Appendix H. Next, a roadmap for how to
proceed was discussed including creating a set of milestones and tasks. The idea
was put forth for the group to interact with the organizing committee of the
2016 NSF Software Infrastructure for Sustained Innovation (SI2) PI workshop in
order to send a software metrics survey to all SI2 and related awardees as a
targeted and relevant set of stakeholders. The five solicitations for software
elements released under the NSF SI2 program all included metrics as a required
component with submitters requested to include {\it ``a list of tangible metrics,
with end user involvement, to be used to measure the success of the software
element developed, \dots''}. These metrics are then reported as part of annual
reports to NSF by the projects. Although neither the proposal text describing
the metrics nor the reported metric results are publicly available, there is
reason to believe that the community will be willing to provide this information
through a survey mechanism. This survey would be created by one of the student
group members. Similarly, it was suggested that a software metrics survey be
sent to the UK SFTF (Software For The Future, led by the Engineering and Physical Sciences Research Council) and TRDF (Tools and Resources Development Fund, led by the Biotechnology and Biological Sciences Research Council) software projects to ask them what metrics would be useful to report. The remainder of the discussion focused mainly on the creation
of a white paper on this topic. This resulted in a paper outline and writing
assignments with the goal of publishing in venues including WSSSPE4, IEEE CiSE (Institute of Electrical and Electronic Engineers Computing in Science and Engineering magazine), or JORS (Journal of Open Research Software). More information about the group discussion is available in Appendix~\ref{sec:appendix_metrics}.

@@

In lieu of a landing page, the Useful Metrics for Scientific Software working
group requests an email be sent to Gabrielle Allen\footnote{email: 
\href{mailto:gdallen@illinois.edu}{gdallen@illinois.edu}} to find out more
about the group's efforts and how to participate.

### 2015-12-20 WSSSPE3/report/wg_main_training.tex
small fix to match bib change
some general cleanup/consistency
moved all emails to footnotes for consistency

\item Workshop on Sustainable Software for Science: Practice and
Experiences (WSSSPE)~\cite{WSSSPE}

@@

Next steps have been identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects.

See Appendix~\ref{sec:appendix_training} for more details about the discussion.

@@

The Training working group requests an email be sent to Nick Jones
\href{mailto:nick.jones@nesi.org.nz}{(nick.jones@nesi.org.nz)} to find out more
about the group's efforts and how to participate.

>>>>

\item Working towards Sustainable Software for Science: Practice and
Experiences (WSSSPE) workshops~\cite{WSSSPE}

@@

Next steps have been identified to quickly test whether there is interest in
establishing a community committed to increasing the degree of coordination
across training projects. See Appendix~\ref{sec:appendix_training} for more details about the discussion.

@@

The Training working group requests an email be sent to Nick Jones\footnote{email: 
\href{mailto:nick.jones@nesi.org.nz}{nick.jones@nesi.org.nz}} to find out more
about the group's efforts and how to participate.
